Child Poverty Interventions

### 2024-06-06 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Additions to ChildPovReduction plotting scripts

workingDir <- "/home/luke/Documents/MINOS/Minos/"
#workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

@@

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 
                                    'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
rel.int <- read_singular_local_out(out.path, 
                                   'ChildPovertyReductionRELATIVE', 
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# rel.int.2 <- read_singular_local_out(out.path,
#                                      'ChildPovertyReductionRELATIVE_2',
#                                      drop.dead = TRUE,
#                                      drop.zero.weight = TRUE)
# abs.int <- read_singular_local_out(out.path, 
#                                    'ChildPovertyReductionABSOLUTE', 
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
```

>>>>

#workingDir <- "/home/luke/Documents/MINOS/Minos/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

@@

```{r, include=FALSE}
#out.path <- here::here('output', 'default_config/')
out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 
                                    'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
# rel.int <- read_singular_local_out(out.path, 
#                                    'ChildPovertyReductionRELATIVE', 
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
rel.int <- read_singular_local_out(out.path,
                                     'ChildPovertyReductionRELATIVE_2',
                                     drop.dead = TRUE,
                                     drop.zero.weight = TRUE)
abs.int <- read_singular_local_out(out.path,
                                   'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
```

### 2024-06-06 minos/outcomes/ChildPovReduction_plots.Rmd
Additions to ChildPovReduction plotting scripts

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

@@

@@

  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

@@

SF12_change_percentage(summary_group = 'whole_pop',
                       scen.list = scen.list.test)
```

@@

SF12_change_percentage(summary_group = 'families',
                       scen.list = scen.list.test)
```

@@

@@

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

SF12_change_ind_trajectories <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

  p1 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_line(data = plot_data, aes(x = year, y = diff_SF_12, group = run_id), alpha = 0.2) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = 'tit') +
    xlab('Year') +
    ylab('Change in SF-12')

  print(p1)
}

@@

  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

```{r "inequality_plots", include=FALSE}
inequality_plots <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

  data$income_quintile <- factor(data$income_quintile)

  # Combine the data
  data_combined <- data %>%
    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))

  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
    geom_smooth(alpha = 0.7) +
    scale_color_manual(name = "Income Quintile", 
                       values = c("red", "blue", "green", "orange", "purple")) +
    scale_linetype_manual(name = "Scenario", 
                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
    labs(title = "SF_12 Scores by Income Quintile",
         subtitle = tit,
         x = "Year",
         y = "Mean SF_12 MCS") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

  # Aggregate data
  agg_data <- data %>%
    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
    group_by(year, income_quintile, scenario) %>%
    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
    spread(scenario, mean_SF_12) %>%
    mutate(difference = Intervention - Baseline)

  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(name = "Income Quintile", 
                      values = c("red", "blue", "green", "orange", "purple")) +
    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
         subtitle = tit,
         x = "Year",
         y = "Difference in SF_12 Score") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

@@

SF12_change_percentage(summary_group = 'whole_pop',
                       scen.list = scen.list.test)

SF12_change_ind_trajectories(summary_group = 'whole_pop',
                             scen.list = scen.list.test)

inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.test)
```

@@

SF12_change_percentage(summary_group = 'families',
                       scen.list = scen.list.test)

SF12_change_ind_trajectories(summary_group = 'families',
                             scen.list = scen.list.test)

inequality_plots(summary_group = 'families',
                 scen.list = scen.list.test)
```

@@

```{r}
#SF12_change_simple <- function(summary_group, scen.list) {

tit <- ' '
# if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
# if (summary_group == 'families') { tit <- 'Families' }

summary_group <- 'whole_pop_income_quint'
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

data$income_quintile <- factor(data$income_quintile)

base.test <- filter(data, scen == 'baseline')
pov.test <- filter(data, scen == 'ChildPovertyReductionRELATIVE_2')

# ggplot(base.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile)) +
#   geom_smooth(alpha = 0.7) +
#   geom_smooth(data = pov.test, aes(x = year, y = SF_12, group = income_quintile, color = income_quintile), linetype = 'dotted')

# Combine the data
data_combined <- data %>%
  mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))

ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
  geom_smooth(alpha = 0.7) +
  scale_color_manual(name = "Income Quintile", 
                     values = c("red", "blue", "green", "orange", "purple")) +
  scale_linetype_manual(name = "Scenario", 
                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
  labs(title = "SF_12 Scores by Income Quintile",
       subtitle = "Comparison of Baseline and Intervention",
       x = "Year",
       y = "Mean SF_12 MCS") +
  theme_minimal() +
  theme(legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

ggplot(data_combined, aes(x = year, y = SF_12, group = scenario, color = scenario)) +
  geom_smooth(alpha = 0.7, aes(linetype = scenario)) +
  facet_wrap(~ income_quintile) +
  scale_color_manual(name = "Scenario", 
                     values = c("Baseline" = "black", "Intervention" = "red")) +
  scale_linetype_manual(name = "Scenario", 
                        values = c("Baseline" = "solid", "Intervention" = "dotted")) +
  labs(title = "SF_12 Scores by Income Quintile",
       subtitle = "Comparison of Baseline and Intervention Scenarios",
       x = "Year",
       y = "SF_12 Score") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

# Calculate the differences
diff_data <- data %>%
  pivot_wider(names_from = scen, values_from = SF_12) %>%
  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline) %>%
  gather(scen, SF_12, baseline, ChildPovertyReductionRELATIVE_2)

ggplot(diff_data, aes(x = year, y = difference, group = income_quintile, color = income_quintile)) +
  geom_line() +
  scale_color_manual(name = "Income Quintile", 
                     values = c("red", "blue", "green", "orange", "purple")) +
  labs(title = "Difference in SF_12 Scores by Income Quintile",
       subtitle = "Intervention Scenario Minus Baseline Scenario",
       x = "Year",
       y = "Difference in SF_12 Score") +
  theme_minimal() +
  theme(legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

# Aggregate data
agg_data <- data %>%
  group_by(year, income_quintile, scen) %>%
  summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
  spread(scen, mean_SF_12) %>%
  mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)

ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(name = "Income Quintile", 
                    values = c("red", "blue", "green", "orange", "purple")) +
  labs(title = "Average Difference in SF_12 Scores by Income Quintile",
       subtitle = "Intervention Minus Baseline",
       x = "Year",
       y = "Difference in SF_12 Score") +
  theme_minimal() +
  theme(legend.position = "right",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

@@

```{r}
inequality_plots <- function(summary_group, scen.list) {

  #summary_group <- 'whole_pop_income_quint'
  #scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

  data$income_quintile <- factor(data$income_quintile)

  # Combine the data
  data_combined <- data %>%
    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))

  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
    geom_smooth(alpha = 0.7) +
    scale_color_manual(name = "Income Quintile", 
                       values = c("red", "blue", "green", "orange", "purple")) +
    scale_linetype_manual(name = "Scenario", 
                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
    labs(title = "SF_12 Scores by Income Quintile",
         subtitle = "Comparison of Baseline and Intervention",
         x = "Year",
         y = "Mean SF_12 MCS") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

  # Aggregate data
  agg_data <- data %>%
    group_by(year, income_quintile, scen) %>%
    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
    spread(scen, mean_SF_12) %>%
    mutate(difference = `ChildPovertyReductionRELATIVE_2` - baseline)

  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(name = "Income Quintile", 
                      values = c("red", "blue", "green", "orange", "purple")) +
    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
         subtitle = "Intervention Minus Baseline",
         x = "Year",
         y = "Difference in SF_12 Score") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.test)

inequality_plots(summary_group = 'families',
                 scen.list = scen.list.test)
```

### 2024-06-06 minos/outcomes/child_poverty_reduction_vis.Rmd
Additions to ChildPovReduction plotting scripts

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

@@

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
# int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

@@

```{r, include=FALSE}
#out.path <- here::here('output', 'default_config/')
out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
# int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
